Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-04-07 Report/ieee_journal.tex
updated
Revert "updated"
This reverts commit 3664d68b10b962e2267a6fe47e1ec19a87ab526c.
nam modified (Appendices)
updated - final - draft
ordered algorithm locations
need to address nam's final comments
latest changes
antti changes
removed-tightness-discussion
Updated color for the revisions
adhi
adhi-calling

\documentclass[11pt,journal,onecolumn,letterpaper]{./../Styles/IEEEtran}

@@

\newtoggle{includereview}
\newtoggle{enable_dist_fig}
\newtoggle{single_column}
\toggletrue{single_column}
\togglefalse{enable_dist_fig}

@@

\begin{IEEEkeywords}
Convex approximations, \ac{MIMO}-\acs{IBC}, \ac{MIMO}-\ac{OFDM}, precoder design, \acs{SCA}, \ac{WSRM}.
\end{IEEEkeywords}

\acresetall

@@

\subsection{\acs{JSFRA} Scheme via \ac{SCA} approach} \label{sec-3.2.1}
\input{problem_formulation}
\input{wsrm_formulation}

@@

@@

\section{Tightness of \ac{SINR} relaxation} \label{a-3}
\review{\input{appendix_tightness}}

\section{Convergence Proof for Centralized Algorithm} \label{sec-3.5}
\review{\input{convergence_centralized}}

\section{Convergence Proof for Distributed Algorithms} \label{sec-dist-conv}
\review{\input{convergence_distributed}}

>>>>

\documentclass[10pt,journal,twocolumn,letterpaper]{./../Styles/IEEEtran}

@@

\newtoggle{includereview}
\newtoggle{enable_dist_fig}
\newtoggle{single_column}
\togglefalse{single_column}
\togglefalse{enable_dist_fig}

@@

\begin{IEEEkeywords}
Convex approximations, \ac{MIMO}-\acs{IBC}, \ac{MIMO}-\ac{OFDM}, precoder design, \acs{SCA}, \acs{WSRM}.
\end{IEEEkeywords}

\acresetall 
\acused{MU}

@@

\subsection{\acs{JSFRA} Scheme via \ac{SINR} Relaxation} \label{sec-3.2.1}
\input{problem_formulation}

\input{wsrm_formulation}

@@

\clearpage

@@

%\section{Tightness of \ac{SINR} relaxation} \label{a-3}
%\input{appendix_tightness}

\section{Convergence Proof for Centralized Algorithm} \label{sec-3.5}
\input{convergence_centralized}

\section{Convergence Proof for Distributed Algorithms} \label{sec-dist-conv}
\input{convergence_distributed}

### 2015-04-07 Report/introduction.tex
updated - final - draft
adhi-calling

%The last mile wireless connectivity poses significant bottleneck in the overall data traffic for the interconnected networks. The main challenges in the wireless networks are due to the scarcity of the available resources either in terms of power or spectrum usage and the complexity of the receiver algorithms which impacts the mobile battery consumption. In order to overcome the receiver complexity, \ac{OFDM} is introduced for the wide band transmissions. To improve data rate, multiple antennas are installed at \acp{BS} and/or at user terminals to avail additional freedom in the form of spatial dimension. The inclusion of \ac{MIMO} technique in wireless networks provides higher data rate or lower outage for the same transmission power and bandwidth.

\acused{MU}

In a network with multiple \acp{BS} serving multiple users, the main driving factor for the transmission are the packets waiting at each \ac{BS} corresponding to the different users present in the network. We consider the problem of transmit precoder design over the space-frequency resources provided by the \ac{MIMO} \ac{OFDM} framework in the downlink \ac{IBC} to minimize the number of queued packets at each \ac{BS}. Since the available resources are shared by multiple users associated with different \acp{BS}, it can be viewed as a resource allocation problem.

@@

\subsubsection*{Main Contributions}
\review{In this paper, we design the precoders jointly across space-frequency resources by minimizing the total number of backlogged packets waiting at the \acp{BS} queues. Since the transmissions are guided by the backlogged packets, the proposed formulation limits the allocations beyond the number of backlogged packets without additional rate constraint. We adopt the \ac{SCA} to solve a sequence of convex subproblems using the first order Taylor approximation due to the nonconvexity imposed by the \ac{DC} constraints.} Initially, we propose centralized \ac{JSFRA} algorithms, which employs the \ac{SCA} for the nonconvex \ac{DC} constraint. The first method is by using the \ac{SINR} expression and the second one is by using the \ac{MSE} equivalence with the rate expression to solve for the optimal precoders. Then we propose distributed precoder designs based on the primal and the \ac{ADMM} methods. Finally, an iterative practical algorithm is proposed to decouple the precoder design across the coordinating \acp{BS} with limited information exchange by solving the \ac{KKT} conditions for the \ac{MSE} reformulation. \review{Note that the joint space-frequency channel matrix can be formed by stacking the channel of each sub-channel in a block-diagonal form for all users}.

>>>>

%The last mile wireless connectivity poses significant bottleneck in the overall data traffic for the interconnected networks. The main challenges in the wireless networks are due to the scarcity of the available resources either in terms of power or spectrum usage and the complexity of the receiver algorithms which impacts the mobile battery consumption. In order to overcome the receiver complexity, \ac{OFDM} is introduced for the wide band transmissions. To improve data rate, multiple antennas are installed at \acp{BS} and/or at user terminals to avail additional freedom in the form of spatial dimension. The inclusion of \ac{MIMO} technique in wireless networks provides higher data rate or lower outage for the same transmission power and bandwidth.
In a network with multiple \acp{BS} serving multiple users, the main driving factor for the transmission are the packets waiting at each \ac{BS} corresponding to the different users present in the network. We consider the problem of transmit precoder design over the space-frequency resources provided by the \ac{MIMO} \ac{OFDM} framework in the downlink \ac{IBC} to minimize the number of queued packets at each \ac{BS}. Since the available resources are shared by multiple users associated with different \acp{BS}, it can be viewed as a resource allocation problem.

@@

\subsubsection*{Main Contributions}
\review{In this paper, we design the precoders jointly across space-frequency resources by minimizing the total number of backlogged packets waiting at the \acp{BS} queues. Since the transmissions are guided by the backlogged packets, the proposed formulation limits the allocations beyond the number of backlogged packets without additional rate constraint. We adopt \ac{SCA} to solve a sequence of convex subproblems using the first order Taylor approximation due to the nonconvexity imposed by the \ac{DC} constraints.} Initially, we propose centralized \ac{JSFRA} algorithms, which employs \ac{SCA} for the nonconvex \ac{DC} constraint. The first method is obtained by relaxing the \ac{SINR} expression and the second one is by utilizing the \ac{MSE} equivalence with the \ac{SINR} expression to solve for the precoders. Then we propose distributed precoder designs based on the primal and the \ac{ADMM} methods. Finally, an iterative practical algorithm is proposed to decouple the precoder design across the coordinating \acp{BS} with limited information exchange by solving the \ac{KKT} conditions for the \ac{MSE} reformulation. \review{Note that the joint space-frequency channel matrix can be formed by stacking the channel of each sub-channel in a block-diagonal form for all users}.
